SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-05 results.tex
Worked on Images, Results Section

PPF yields a speedup of \textbf{42.8\%} over the baseline. This is equivalent
to \textbf{7.8\%} over DA-AMPM, \textbf{9.7\%} over BOP and \textbf{6.92\%}
over SPP.  Out of the 95 simpoints developed for SPEC CPU 2017, PPF nearly
matches or outperforms most of the prefetchers on 91 simpoints.  PPF fails to
match the improvement offered by BOP only for {\tt 607.cactuBSSN\_s} and {\tt
654.roms\_s}.

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on the
trace {\tt 602.gcc\_s-2226B}.  This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher -- BOP.  In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt 623.xalancbmk\_s} and {\tt
649.fotonik3d\_s} benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
On the full SPEC CPU 2017 suite, PPF improves the baseline by \textbf{20.9\%},
which is \textbf{3.44\%} better than the next best prefetcher -- SPP.

@@

\textbf{Coverage}\newline
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{4Core_SPEC2017}
\caption{Normalized speedup for 4-core workloads}
\label{Fig:4Core_SPEC2017}
\end{figure}

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.

\textit{4-core environment} Figure~\ref{Fig:4Core_SPEC2017}(a) shows a
comparison of speedups obtained on 4-core mixes of a memory intensive subset
SPEC CPU 2017.  We plot all 4 prefetchers, normalized to the baseline.  The
workloads have been sorted in increasing order of the speedup.  PPF offers a
speedup of \textbf{51.7\%} on these traces, and improvement of \textbf{11.9\%}
over the baseline SPP, \textbf{10.2\%} over the next DA-AMPM, and
\textbf{17.4\%} over BOP.

On a different set of fully random SPEC CPU 2017 4-core mixes, PPF provides an
IPC speedup of \textbf{26.2}\% over the baseline, which is an improvement of
\textbf{5.7}\% over SPP.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{8Core_SPEC2017}
\caption{Normalized speedup for 8-core workloads}
\label{Fig:8Core_SPEC2017}
\end{figure}

\textit{8-core environment} The sorted comparison of speedups on the memory
intensive 8-core mixes is shown in Figure~\ref{Fig:8Core_SPEC2017}.  PPF
improves baseline performance by \textbf{38.6\%}, an improvement of
\textbf{10.7\%} over SPP.  For a random set of SPEC CPU 2017 mixes, PPF
improves performance by \textbf{23.6\%} over the baseline, corresponding to
\textbf{4.8\%} over SPP.  This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.

@@

\begin{figure}[ht]
\includegraphics[width=\columnwidth]{AddnConstr}
\caption{IPC speedup for Small LLC and Low BW}
\label{Fig:AddnConstr}
\end{figure}

@@

% djimenez: cite cloudsuite here? do we have a reference?

@@

% djimenez: is the improvement over BOP and DA-AMPM exactly the same 9.86%
% here? that's weird.

Figure~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and
PPF on traces from SPEC CPU 2006, along with the overall geometric mean over
the whole suite and over a memory-intensive subset.  PPF provides a speedup of
\textbf{46.1\%} over the baseline on the memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.66\%} over SPP and
\textbf{9.86\%} over BOP and DA-AMPM.  On the whole of the SPEC CPU 2006
suite, the speedup is \textbf{22.4\%}, an improvement of \textbf{3.34\%} over
SPP.

>>>>

PPF yields a geometric mean speedup of \textbf{42.8\%} over the baseline. 
This is equivalent to \textbf{7.8\%} over DA-AMPM, \textbf{9.7\%} over BOP 
and \textbf{6.92\%} over SPP.  Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints.  PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s}.

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on the
trace {\tt 602.gcc\_s-2226B}.  This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher -- BOP.  In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt 623. xalancbmk\_s} and {\tt
649.fotonik3d\_s} benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{20.9\%}, which is \textbf{3.44\%} better 
than the next best prefetcher -- SPP.
\newline

@@

\noindent \textbf{COVERAGE}
\newline
Prefetcher coverage is defined as the ratio of the number of misses avoided
through prefetching to the number of misses with no prefetching.

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{4Core_SPEC2017}
\caption{Normalized Speedup for 4-core SPEC CPU 2017 Workloads}
\label{Fig:4Core_SPEC2017}
\end{figure*}

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.
\newline

\noindent \textbf{4-CORE ENVIRONMENT}
\newline
Figure~\ref{Fig:4Core_SPEC2017}(a) shows a
comparison of speedups obtained on 4-core mixes of a memory intensive subset
SPEC CPU 2017.  We plot all 4 prefetchers, normalized to the baseline.  The
workloads have been sorted in increasing order of the speedup.  PPF offers a
speedup of \textbf{51.7\%} on these traces, and improvement of \textbf{11.9\%}
over the baseline SPP, \textbf{10.2\%} over the next DA-AMPM, and
\textbf{17.4\%} over BOP.

On a different set of fully random SPEC CPU 2017 4-core mixes, PPF provides an
IPC speedup of \textbf{26.2}\% over the baseline, which is an improvement of
\textbf{5.7}\% over SPP.
\newline

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{8Core_SPEC2017}
\caption{Normalized Speedup for 8-core SPEC CPU 2017 Workloads}
\label{Fig:8Core_SPEC2017}
\end{figure*}

\noindent \textbf{8-CORE ENVIRONMENT}
\newline
The sorted comparison of speedups on the memory
intensive 8-core mixes is shown in Figure~\ref{Fig:8Core_SPEC2017}.  PPF
improves baseline performance by \textbf{38.6\%}, an improvement of
\textbf{10.7\%} over SPP.  For a random set of SPEC CPU 2017 mixes, PPF
improves performance by \textbf{23.6\%} over the baseline, corresponding to
\textbf{4.8\%} over SPP.  This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.

@@

\begin{figure}[ht]
\begin{adjustwidth}{-1cm}{}
  \includegraphics[width=1.2\columnwidth]{AddnConstr}
  \caption{IPC speedup for Small LLC and Low BW}
  \label{Fig:AddnConstr}
\end{adjustwidth}
\end{figure}

@@

% djimenez: cite cloudsuite here? do we have a reference?
% [EB]: Resolved. Cited "Clearing the clouds: A study of emerging 
%        scale-out workloads on modern hardware" in methodology

@@

% djimenez: is the improvement over BOP and DA-AMPM exactly the same 9.86%
% here? that's weird.
% [EB] Resolved. Increased precision of values. But yes, BOP / DA-AMPM 
% have really close numbers for SPEC 2006

Figure~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and
PPF on traces from SPEC CPU 2006, along with the overall geometric mean over
the whole suite and over a memory-intensive subset.  PPF provides a speedup of
\textbf{46.1\%} over the baseline on the memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.66\%} over SPP and
\textbf{9.88\%} over DA-AMPM and \textbf{9.82} over BOP.  On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{22.4\%}, an improvement 
of \textbf{3.34\%} over SPP.
